Designing Turk Experiments for Visual Statistical Inference

### 2013-06-22 paper_turk.tex
experiment design

If a lineup is created from actual observed data, the web application presented in Section \ref{sec:web_application} can be used to evaluate it. In that case we do not need to design a simulation experiment. This section will be useful when a simulation experiment is needed to examine different plot types as test statistics and compare the power of visual test \citep{majumder:2013}. To examine the effectiveness of certain plots in displaying the data one might want to design an experiment with lineup \citep{heike:2012}. In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to evaluate a lineup.

\subsection{Selecting Parameter to Simulate Lineup} \label{sec:parameter_selection} In any experimental design we need to have some control. For a simulation experiment with lineup, this refers to the parameter related to a lineup. This depends on what the purpose of the experiment is. For example, to compare the power of a parametric test one may fix the parameter specified by alternative hypothesis and generate data from that model. This data can be considered as the observed data. A lineup can be created by placing this observed data plot on a lineup where rest of the data plots come from the model specified by the null model \citep{majumder:2013}.

@@

{\bf Quantiles of $p$-value approach:} For a simulated observed data set we can obtain the $p$-value associated to testing $H_0: \beta=0$. The distribution of $p$-value is uniform under null hypothesis but under alternative it has a right skewed distribution. Figure~\ref{fig:dist_pvalue} shows the distribution  of $p$-values for sample size $n$=300, regression slope $\beta$=3 and error standard deviation $\sigma$=12. If we generate a data set randomly there is a 21\% chance that the data will show a $p$-value of 0.25 or more even though we generated data set with non-zero $\beta=3$. We need to make sure that the simulated data does not come from this extreme end. On top of that we want some replication so that this extreme effect can be controlled at some level. For this example we intend to pick three replications.

@@

In this approach we generate 1000 data sets from the model of interest and obtain $p$-values for each data set after fitting the same model. We construct 3 blocks of $p$-values such as (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the $p$-values. We randomly select three data sets that have corresponding $p$-values in the above quantile range.  Notice that if we like to have three replications of plots, we will have observed data sets with smaller $p$-values as the distribution is highly right skewed as well as the 33th and 66th percentiles of p-values are 0.0101 and 0.077 respectively. So, another option may be to take the mid points of those quantile ranges and pick the data sets that have those p-values. \\

@@

All of these three approaches discussed above has some problems. Kolmogorov method does not necessarily make sure that estimated parameters are close to the true parameters. On the other hand closeness of estimated parameters does not make sure that $p$-value is small enough when we should reject the null hypothesis. Only the quantiles approach seems reasonable as it has much control over $p$-values and it gives similar data sets that has closest parameter estimates. So we suggest the quantiles of $p$-value approach to generate observed data with specific effect size.

@@

\subsection{Test and Training Lineup} Some lineups should be presented to the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment. It is important to setup this properly. The training lineups should be easy and feedback should be provided right after the response is received. The purpose is to give them an idea how the actual task would look like.

@@

Other things that needs to be considered include number of training lineups, how the lineups should be shown. Training should not take much longer. Two or three lineups can provide enough training. The training lineups should be easy to evaluate and they should be randomly selected from a very small number of lineups. That may produce repetition which may help the MTurk workers to retest their skill on the lineup the might have a wrong selection before.

@@

It is helpful if some example lineups are presented with the experimental description. Example lineup on the homepage should be of size three or four so that more than one lineup can be placed on the homepage. This helps the worker decide whether they are willing to participate the experiment at all.

\subsection{Plan for a Turk Task} \label{sec:task_plan} To make a good use of MTurk crowd source, it is important to split any big project into small pieces or Task. To present each task for the workers to do, a Human Intelligence Task or HIT needs to be designed which includes crisp and clear instructions of the task, descriptions of specific input and output desired and payment information. To design a HIT for lineups to be evaluated we need to consider the following issues;

@@

\item {\bf Data input:} For lineup experiments data input means mainly the lineups that are going to be presented for evaluations. Lineups may be presented in some sequence or completely at random. We need to decide whether a test lineup will be included or not in the pool of lineups going to be presented. Some other inputs may accompany with each lineup. Those include lineup question, how many lineups to be evaluated by the worker etc. Anything that the worker will see changing with each lineup is considered as data input to the worker. For different experimental needs this input may be different. For example, one may decide to let the worker know if each evaluation made is correct or wrong right after the feedback. This is an input for the worker.

\item {\bf Data output:} This means the data collected from the MTurk workers. That includes mainly the response on lineup question. Single or multiple responses can be requested for each lineup. Other optional data that may be collected are as follows;

>>>>

If a lineup is created from actual observed data, the web application presented in Section \ref{sec:web_application} can be used to evaluate it. In that case we do not need to design a simulation experiment. This section will be useful when a simulation experiment is needed to examine different visual test statistics and compare the power \citep{majumder:2013}. To examine the effectiveness of certain plots in displaying the data one may want to design an experiment with lineup \citep{heike:2012}. In any cases, two major considerations are choice of parameters to simulate lineup and number of people needed to evaluate a lineup.

\subsection{Selecting Parameter to Simulate Lineup} \label{sec:parameter_selection} In any experimental design we need to have some control. For a simulation experiment with lineup, this refers to the parameter related to a lineup. This depends on what the purpose of the experiment is. For example, to compare the power of a parametric test one may fix the parameter specified by alternative hypothesis and generate data from that model. This data can be considered as the observed data. A lineup can be created by placing this observed data plot in a layout where rest of the data plots come from the model specified by the null model \citep{majumder:2013}.

@@

{\bf Quantiles of $p$-value approach:} For a simulated observed data set we can obtain the $p$-value associated to testing $H_0: \beta=0$. The distribution of $p$-value is uniform under null hypothesis but under alternative it has a right skewed distribution. Figure~\ref{fig:dist_pvalue} shows the distribution  of $p$-values for sample size $n$=300, regression slope $\beta$=3 and error standard deviation $\sigma$=12. If we generate a data set randomly there is a 21\% chance that the data will show a $p$-value of 0.25 or more even though we generated data set with non-zero $\beta=3$. We need to make sure that the simulated data does not come from this extreme end. Additionally, we want some replications so that this extreme effect can be controlled at some level. For this example we intend to pick three replications.

@@

In this approach we generate 1000 data sets from the model of interest and obtain $p$-values for each data set after fitting the same model. We construct 3 blocks of $p$-values such as (0.0-$q_{33}$), ($q_{33}$-$q_{66}$), ($q_{66}$-1) where $q_i$ is the $i$th percentile in the distribution of the $p$-values. We randomly select three data sets that have corresponding $p$-values in the above quantile range.  Notice that if we like to have three replications of plots, we will have observed data sets with smaller $p$-values as the distribution is highly right skewed as well as the 33th and 66th percentiles of p-values are 0.0101 and 0.077 respectively. So, another option may be to take the mid points of those quantile ranges and pick the data sets that produce those p-values. \\

@@

All of these three approaches discussed above have some problems. Kolmogorov method does not necessarily make sure that estimated parameters are close to the true parameters. On the other hand closeness of estimated parameters does not make sure that $p$-value is small enough when we should reject the null hypothesis. Only the quantiles approach seems reasonable as it has much control over $p$-values and it gives similar data sets that has closest parameter estimates. So we suggest the quantiles of $p$-value approach to generate observed data with specific effect size.

@@

\subsection{Test and Training Lineup} Some lineups should be displayed for the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment. It is important to setup this properly. The training lineups should be easy and feedback should be provided right after the response is received. The purpose is to give them an idea how the actual task would look like. The worker may or may not like to try the training lineups.

@@

Other things that needs to be considered include number of training lineups and how the lineups should be shown. Training should not take much longer. Two or three lineups can provide enough training. The training lineups should be easy to evaluate and they should be randomly selected from a very small number of lineups. That may produce repetition which may help the MTurk workers to retest their skills on the lineup they might have a wrong selection before.

@@

It is helpful if some example lineups are presented with the experimental description. Example lineup does not have to be of the size similar to the actual lineup. it can be of size three or four so that more than one lineup can be placed on a page for demonstration of the task. This helps the worker decide whether they are willing to participate the experiment at all.

\subsection{Plan for a Turk Task} \label{sec:task_plan} To make a good use of MTurk crowd source, it is important to split any big project into small pieces or Tasks. To present each task for the workers to do, a Human Intelligence Task or HIT needs to be designed which includes crisp and clear instructions of the task, descriptions of specific input and output desired and payment information. To design a HIT for lineups to be evaluated we need to consider the following issues;

@@

\item {\bf Data input:} For lineup experiments input data  mainly refer to the lineups that are going to be presented for evaluations. Lineups may be presented in some sequence or completely at random. We need to decide whether a test lineup will be included or not in the pool of lineups going to be presented. Some other inputs may accompany with each lineup. Those include lineup question, how many lineups to be evaluated by the worker etc. Anything that the worker will see changing with each lineup is considered as data input to the worker. For different experimental needs this input may be different. For example, one may decide to let the worker know if each evaluation made is correct or wrong after the feedback has been submitted. This is an input for the worker.

\item {\bf Data output:} This means the data to be collected from the MTurk workers. That includes mainly the response on lineup question. Single or multiple responses can be requested for each lineup. Other optional data that may be collected are as follows;
